---
title: "Report III"
author: "Ma siteng(simon), Liang shuang, Liu zhening(NiuNiu), Zhang yu"
date: "2020/11/3"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(reshape2)
require(ggplot2)
require(ggthemes)
theme_set(theme_minimal())
require(GGally)
require(ggExtra)
```

## Operations Analysis of Assignment III
This assignment consists in a single task: load the bright.Rdata
data and, assuming that the number of looks is L0 = 1:

1. Fit the SAR Gamma model Γ (μ, L0) (notice that you have to estimate only μ);
2. Fit the model (you have to estimate α, γ).$$𝒢_I^0(α, γ, L0)$$
Show two results in this part:  
• Moments estimators  
• Maximum Likelihood estimators 

“Fitting a model”, in this assignment, means:  
• reporting the estimates (one for the Γ (μ, L0) model), and two pairs for the model)  
• showing a histogram of the data along with the three estimated densities.$$𝒢_I^0(α, γ, L0)$$  

the density of Gamma is:

$$
\int_0^{Inf} t^{(x-1)}exp(-t)dt
$$

The (SAR) Gamma distribution is

$$Z \sim {} \Gamma(\mu, L)$$
density:

$$
f_\Gamma(z; L, \mu)=\frac{L^L}{\mu^L\Gamma(L)}z^{L-1}exp{(\frac{-Lz}{\mu})}
$$
if L = 1

the density will be:

$$
f_\Gamma(z; 1, \mu)=\frac{1^1}{\mu^1\Gamma(1)}z^{1-1}exp{(\frac{-1z}{\mu})}
$$
$$
\Gamma(1)=\int_0^{Inf} t^{(1-1)}exp(-t)dt=1
$$
$$
\Gamma(n+1)=n!
$$
$$
\Gamma(n+1)=n\Gamma(n)
$$

which equal to:

$$
f_\Gamma(z; 1, \mu)=\frac{1}{\mu}exp{(\frac{-z}{\mu})}
$$

moment estimation for gamma:

$$
E(z)=\int_0^{Inf}zf_\Gamma(z;1,\mu)dz=\int_0^{Inf}\frac{z}{\mu}exp(\frac{-z}{\mu})dz=\mu
$$
maximum likelihood estimation:

$$
L=\prod_{i=1}^n(\frac{1}{\mu}e^{(\frac{-z_i}{\mu})})
$$

$$
lnL=-nln{\mu}+\frac{\sum_{i=1}^{n}-z_i}{\mu}
$$

$$
\frac{\mathrm{d}lnL}{\mathrm{d}\mu}=-\frac{n}{\mu}+\frac{\sum_{i=1}^{n}z_i}{\mu^2}=0
$$
$$
\hat\mu=\frac{\sum_{i=1}^nz_i}{n}
$$

```{r load bright.data}
load("../../Data/R/bright.Rdata")
```

the μ should be:

```{r}
bright.v = as.vector(bright)
bright.df = data.frame(as.vector(bright))

u = mean(bright.v)
print(u)
```

The density for (SAR) gamma in this bright.

```{r Moments estimators}
bright.v = as.vector(bright)
bright.df = data.frame(as.vector(bright))

u = mean(bright.v)

f <- function(x){1/u*exp(1)^(-x/u)}
x <- seq(0, 5000000, length.out=5000)
y = f(x)

y.df = data.frame(as.vector(y))
xy.df<-data.frame(x=x,y)

ggplot(xy.df,aes(x=x,y))+
  geom_line(colour="orange", size=1)+
  ggtitle("Bright gamma distribution")

ggplot(bright.df, aes(x=bright)) +
  geom_histogram(aes(y=..density..),
                 col="blue", fill="white")+
  geom_density(col="red", size=1)+
  scale_x_log10()
```

## The G0I distribution
The G0I distribution is:
$$
f_z(z;\alpha,\gamma,L)=\frac{L^L\Gamma(L-\alpha)}{\gamma^\alpha\Gamma(L)\Gamma(-\alpha)}\frac{z^L}{(\gamma+Lz)^{L-\alpha}}
$$
when L=1:

$$
f_z(z;\alpha,\gamma,1)=\frac{\Gamma(1-\alpha)}{\gamma^\alpha\Gamma(-\alpha)}\frac{z}{(\gamma+z)^{1-\alpha}}
$$
$$
f_z(z;\alpha,\gamma,1)=\frac{-\alpha}{\gamma^\alpha}\frac{z}{(\gamma+z)^{1-\alpha}}
$$
$$
E(z^k)=(\frac{\gamma}{L})^k\frac{\Gamma(-\alpha-k)}{\Gamma(-\alpha)}\frac{\Gamma(L+k)}{\Gamma(L)}
$$

when L=1, k=1:

$$
E(z)=\gamma\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}
$$
$$
E(z)=\frac{\gamma}{-\alpha-1}
$$
when L=1, k=2
$$
E(z^2)=2\gamma^2\frac{\Gamma(-\alpha-2)}{\Gamma(-\alpha)}
$$
$$
E(z^2)=\frac{2\gamma^2}{(-\alpha-1)(-\alpha-2)}
$$

$$
D(z)=E[(z-E(z))^2]=E(z^2)-[E(z)]^2
$$

$$
D(z)=\frac{-\alpha\gamma^2}{(-\alpha-1)^2(-\alpha-2)}
$$

we can solve α and $\gamma$ by E(z) and E(z^2), or by E(z) and D(z).

## The first solution(E(z) and E(z^2)):
Let m1 = E(z), m2 = E(z^2)  
We will get:

$$
\hat\alpha=-2-\frac{2}{m2/m1^2}
$$
$$
\hat\gamma=m1(2+\frac{2}{2m2/m1^2})
$$

the α and $\gamma$ in GOI should be:

```{r}
bright.v = as.vector(bright)
bright.df = data.frame(as.vector(bright))

m1 = mean(bright.v)
m2 = mean(bright.v^2)
m3 = m2/m1^2

alpha = -2-2/(m3)

pgamma = m1*(2+2/(m3))

print(alpha)
print(pgamma)

```

## The second solution(E(z), D(z)):
Let m1=E(z), m2=D(z), m3 = m2/m1^2  
We will get:

$$
\hat\alpha=\frac{2m_{3}}{1-m_{3}}
$$
$$
\hat\gamma=-m_1\frac{1+m_{3}}{1-m_{3}}
$$
the α and $\gamma$ in GOI should be:

```{r}
bright.v = as.vector(bright)
bright.df = data.frame(as.vector(bright))

m1 = mean(bright.v)
m2 = var(bright.v)
m3 = m2/m1^2

alpha = 2*m3/(1-m3)

pgamma = -m1*(1+m3)/(1-m3)

print(alpha)
print(pgamma)

```

```{r}
bright.v = as.vector(bright)
bright.df = data.frame(as.vector(bright))

m1 = mean(bright.v)
m2 = var(bright.v)
m3 = m2/m1^2

alpha = 2*m3/(1-m3)

pgamma = -m1*(1+m3)/(1-m3)

f_z <- function(z){(-alpha)/(pgamma^alpha)*(z)/(pgamma+alpha)^(1-alpha)}

x <- seq(.1, 1e+8, length.out=50000)

y <- f_z(x)

ggplot(data= NULL, aes(x = x, y = y)) +
  geom_line(color = "green", size=2)+
  scale_x_log10()

ggplot(bright.df, aes(x=bright)) +
  geom_density(col="red", size=1)+
  scale_x_log10()

```


